Descriptive_Stats

### 2023-07-30 Code/RankComparison.Rmd
Added explanations to code

```{r}
nations <- read.csv("../Data/ClusrankNatvsWorld.csv")
colnames(nations) <- c("Time", "Athlete", "Year")
```

Keep the linewidth under 80. Otherwise the code lines are not complete in the
generated pdf files.

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations,
                alternative = "greater", method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations,
                alternative = "greater", method = "ds",
                exact = TRUE, B = 10000)
```
```{r}
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, method = "ds",
                exact = TRUE, B = 10000)
```

```{r}
comp <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Time", "Athlete", "Year")
#View(comp)
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                method = "ds")

@@

```{r}
nations_noprelim <- read.csv("../Data/Clusrank2019vs2022PrelimsOnly.csv")
colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
                alternative = "greater", method = "ds")
```

>>>>

The code below reads in the data comparing the 2022 National Competitions to the 2022
World Championships.
```{r}
national <- read.csv("../Data/ClusrankNatvsWorld.csv")
colnames(national) <- c("Time", "Athlete", "Stage")
```

The code below performs two clustered Wilcox tests, the first one without using
exact = True, and the second one with exact = True and 10,000 random
permutations. The tests compare the times and group by the Stage of the
competition which in the data is coded as 1 if it was a national championship
and 2 if it was the world championships. The tests cluster by athlete, of which
for each dataset an integer from 1-15 is used (the values are not significant).
For more information about the "ds" method, please look at the Rank-based
Comparison subsection of the Methods section of the paper or at this link here:
https://www.jstatsoft.org/article/view/v096i06.  The second test also includes
exact = TRUE which is used when sample sizes are small (as they are in this
case), additionally the number of random permutations (B) is set to be 10,000.

```{r}
library(clusrank)
clusWilcox.test(Time, group=Stage, cluster = Athlete, data = national,
                method = "ds")

clusWilcox.test(Time, group=Stage, cluster = Athlete, data = national,
                method = "ds",
                exact = TRUE, B = 10000)
```

The code below reads in the data comparing the 2019 and 2022 World Championships.
```{r}
comp <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Time", "Athlete", "Year")
#View(comp)
```

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (1 if 2019 and 2 if 2022).
```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                method = "ds")

@@

This is seeing what would happen if we remove prelims, the sample sizes in the
test become very small: 26 observations and 9 clusters.
```{r}
nations_noprelim <- read.csv("../Data/Clusrank2019vs2022PrelimsOnly.csv")
colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
                method = "ds", 
                exact = TRUE, B = 10000)
```
